% TODO rename: Tools and Research ?


%TODO
% now we already have 50 pages of theory
% come back to research question
% give a short overview of related research: list of papers and what they are doing
% move WPT and GA back to Web performance chapter

\chapter{Related Work}
\label{chapter:related_work}

\begin{itemize}
	\item Last chapter...
	\item This chapter: Describe shortly all sections from this chapter
	\item In the next chapter...
\end{itemize}

\begin{itemize}
\item This chapter should list research which covers and explores questions relevant for this thesis, such as:
	\begin{itemize}
	\item Metrics: New metrics, meaning of metrics, difficulties of defining metrics, etc.
	\item Overview, evaluation and comparison of measurement tools and methods
	\item If available: Impact of RUM on performance
	\end{itemize}
\end{itemize}





\section{Research}


\begin{itemize}
\item Research exists about topics like: ....
\item Here i will provide a list of in my eyes relevant papers, summaries them and discuss why this is important for my research
\end{itemize}

% TODO: Think about categorising papers


\subsection{some title for first category}

% 2014 Singal: WEB ANALYTICS: STATE-OF-ART & LITERATURE ASSESSMENT
\paragraph{2014 Singal}

I.
- Describes history of web analytics and tools
- Provides definitions and taxonomy for metrics
- Describes log file vs page tagging
- Describes KPIs

II.
- Lit. overview for KPIs and Web Metrics
- Lit. overview for "Trust"
- Lit. overview for "Fuzzy"
-> What are does categories?


III.
- Some other literature worth mentioning


IV.
- Describes 8 open challenges for researchers


% ---------------------------------------------


\paragraph{2015 Bekavac}

- Two parts:
	- 1: Some general overview of web analytics, tools and metrics, KPIs etc
	- 2: Empirical study about employees satisfaction of used web analytics tools

1: 
- 9 web business models and 5 common goals
- Hypothesis: Web analytics tools track and improve a user’s satisfaction with web-based business models.
- Web anayltics defintion. Log files vs Site Tagging
- Web Analytics process
- Tools: 5 categories, Process of selecting tool, Table with features of different tools
- Web metrics categories, Table with business models and their KPIs

2:
- Which tools are used for which purpose / Activity
- Users satisfaction



% ---------------------------------------------


\subsection{Research about Tools}



% https://www.kaushik.net/avinash/web-analytics-tool-selection-three-questions-to-ask-yourself/
\paragraph{Kaushik 2007}
- Provides 3 questions which help to choose web analytics tools


% ---------------------------------------------


% 2011 Nakatani: A web analytics tool selection method: an analytical hierarchy process approach
\paragraph{2011 Nakatani}

- Gives some arguments why web analytics is important for business
- Provides different categorizations for web analytics tools
- Gives pros and cons of log file analysis and page tagging
- Provides tool selection method based on AHP (Analytic Hierarchy Process)

"Web analytics tools collect click-stream data, track users navigation paths, process and present the data as meaningful information.
- Categorizations:
1: By 4 different data collection methods
2: SaaS vs in-house
3: mobile vs non-mobile
4: Time lag




% ---------------------------------------------


% 2013 Wang: WProf: Profiler / new tool for finding bottlenecks
% - PLT metric
% - How page loading works, CRP, dependencies
% - They create WProf as a tool to analyse dependencies and performance bottlenecks




% ---------------------------------------------


% 2016 Kaur: Tool comparison
\paragraph{2016 Kaur}
% This paper evaluated the university websites of Punjab using four automated tools and gives the comparative results of various factors using these tools.
% -





% 2009 Jansen ch. 6.3
% - paraphrases 10 tips by Kaushik... i would neet to cite them directly


% Croll 2009 Choosing a analytics platform p. 144
- free vs paid
- real time vs long term
- hosted vs in-house
- data portability


% 2011 Marek: Choose a program


% 2015 Bekavac --> Move this to related work ??
% - 5 categories of tools
% - Process of selecting tool
% - Table with features of tools


% 2016 Bartuskova: 1.2 Services for Website Speed Testing



% 2019 Kumar
- free / open source tools
- proprietary tools
- Service Hosted Software
- GA most popular one


% 2020 Quintel: Matomo --> put this to related work ??
% Lighthouse Performance Scoring ?




% Tools: Kessler 2016 p. 576 ??




% ---------------------------------------------


\subsection{Research about Metrics}


Categorizations as seen in section X.


% 2018 Netravali: Ready Index: new metric




% 2019 Enghard Pitfalls







- Dont know:
% 2015  Cito: IDENTIFYING WEB PERFORMANCE DEGRADATIONS THROUGH SYNTHETIC AND REAL-USER MONITORING

% 2016 Bartuskova: Our results indicate that the choice of service and location affects significantly results of website speed testing.






















